### 2023-10-27 introduction/contributions.tex
Diogo correction introduction

\begin{itemize}
  \item I created a script that can generate spice netlists for \acps{LSTM} or feed forward \aclp{NN} of any size and importing weights as resistance values from a specified file containing the architecture and the weights.
  \item The script can generate an \ac{LSTM} capable analog circuit was created and ran in virtuoso giving encouraging results.
  \item The script can also generate an \ac{GRU} capable analog circuit was created and ran in virtuoso.
  \item I developed an analog activation function circuit that supports \ac{tanh} and sigmoid ranges working at $1.8V$.
  \item I recreated a \acp{VMM} capable analog circuit using a matrix of memristors.
  \item I designed a memory cells used to store analog data for a short amount of time, they are used the \ac{LSTM} and \ac{GRU} circuits.
  \item I coded in python \cite{python} (tensorflow library\cite{tensorflow}) to create a piece wise functions to reproduce in the tensorflow the analog activation functions.
  \item I used Cadence's Virtuoso to run software simulation of different \acp{NN} capable analog circuits.
\end{itemize}

>>>>

\begin{itemize}
  \item I created a script that can generate spice netlists for \acps{LSTM} or feed forward \aclp{NN} of any size and importing weights as resistance values from a specified file containing the architecture and the weights.
  \item The script can generate an \ac{LSTM} capable analog circuits and then run a simulation of the circuit in virtuoso giving encouraging results.
  \item The script can also generate an \ac{GRU} capable analog circuits and then run a simulation of the circuit in virtuoso.
  \item I developed an analog activation function circuit that supports \ac{tanh} and sigmoid ranges working at $1.8V$.
  \item I recreated a \acp{VMM} capable analog circuit using a matrix of memristors.
  \item I designed a memory cells used to store analog data for a short amount of time, they are used the \ac{LSTM} and \ac{GRU} circuits.
  \item I coded in python \cite{python} (tensorflow library\cite{tensorflow}) to create a piece wise functions to reproduce in the tensorflow the analog activation functions.
  \item I used Cadence's Virtuoso to run software simulation of different \acp{NN} capable analog circuits.
  \item A paper is being prepared to report the advancements made in this work.
\end{itemize}

### 2023-10-27 introduction/motivation.tex
Diogo correction introduction

Another use for \ac{AI} that works great in embedded use is for camera relocalization \cite{videoReloc}. That is useful especially for \ac{VR} headsets that need to know their location in the room. The embedded chip would allow this computation to be much faster than other methods, and thus give more realistic results.

@@

The focus of this thesis is to create a working simulation of an analog \ac{LSTM} circuit using Cadence's Virtuoso as simulation software. Having those preliminary results would allow to fabricate and test such a chip. Once a working prototype is manufactured, such a circuit could highly improve embedded \ac{AI} use.

>>>>

Another use for \ac{AI} that works great in embedded use is for camera enhanced 3D camera localization \cite{videoReloc}. That is useful especially for \ac{VR} headsets that need to know their location in the room. The embedded chip would allow this computation to be much faster than other methods, and thus give more realistic results.

@@

The focus of this thesis is to create a working simulation of an analog \ac{LSTM} and \ac{GRU} circuit using Cadence's Virtuoso as simulation software. Having those preliminary results would allow to fabricate and test such a chip. Once a working prototype is manufactured, such a circuit could highly improve embedded \ac{AI} use.

### 2023-10-27 introduction/outline.tex
Diogo correction introduction

All the technologies used and, thus are required to know in order to understand the thesis are detailed in the state of the art.

Next the work that was done for the thesis is goign to be thoroughly explained. Starting with the different circuit that were designed for the thesis. Then the different scripts and python code that were created, either to run the digital \acp{NN} or to generate the analog system into a netlist.

>>>>

In \cref{cap:state}, all the technologies used and thus required to know in order to understand the thesis are detailed in the state of the art.

Next, in \cref{cap:design}, the work that was done for the thesis is going to be thoroughly explained. Starting with the different circuit that were designed for the thesis. Then the different scripts and python code that were created, either to run the digital \acp{NN} or to generate the analog system into a netlist.

Then \cref{cap:results} contains the results, obtained from the digital inference and the analog simulation, from both the number of airline passenger and the \ac{C. elegans} datasets.

Finally, in \cref{cap:conclusions}, the conclusions and improvements that can be made to the different parts of the thesis.
